Refunctionalization of Abstracting Abstract Machines (Functional Pearl)

### 2018-03-16 paper.tex
update

%% Title information
\title{Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Filling the Gap Between Abstracting Abstract Machines and Abstracting Definitional Interpreters}        %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Abstracting abstract machines (AAM) is a systematic methodology 
  for constructing abstract interpreters that are derived from concrete
  small-step abstract machines. Recent progress applies the same idea 
  on definitional interpreters and obtains big-step 
  abstract definitional interpreters (ADI) written in monadic style.
  Danvy shows the correspondence between concrete abstract machines and interpreters.
  Yet, the relations between small-step abstracting abstract machines and 
  big-step abstracting definitional interpreters is not well studied.

  In this paper, we show their correspondence and how to syntactically transform small-step 
  abstract abstract machines into big-step abstract definitional 
  interpreters.
  The transformations include fusing, disentangling, refunctionalizing 
  and monadification (or un-CPS to direct-style with delimited continuations). 
  All of them properly handle the 
  collecting semantics and the non-determinism of abstract interpretation. 
  After each transformation, we also obtain an intermediate form of 
  abstract interpreter.

  Following the idea that evaluation contexts are defunctionalized 
  continuations, we also found that refunctionalization sequentializes the 
  non-deterministic abstract evaluation.
  Remarkably, we reveal how precise call/return matching in control-flow 
  analysis can be obtained by properly refunctionalizing a small-step abstract interpreter.
  As well as we explain how it been lost by defunctionalizing the higher-order
  continuations into an first-order data type.

  TODO: Maybe something Shiver's formulation of CFA in denotational style.

\end{abstract}

>>>>

%% Title information
%\title{Pushdown Control-Flow Analysis via Refunctionalization (Functional Pearl)}         %% [Short Title] is optional;
\title{Refunctionalization of Abstracting Abstract Machines (Functional Pearl)}         %% [Short Title] is optional;
                                        %% when present, will be used in
                                        %% header instead of Full Title.
%\titlenote{with title note}             %% \titlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'
\subtitle{Filling the Gap Between Abstracting Abstract Machines and Abstracting Definitional Interpreters}        %% \subtitle is optional
%\subtitlenote{with subtitle note}       %% \subtitlenote is optional;
                                        %% can be repeated if necessary;
                                        %% contents suppressed with 'anonymous'

@@

%% Abstract
%% Note: \begin{abstract}...\end{abstract} environment must come
%% before \maketitle command
\begin{abstract}
  Abstracting abstract machines (AAM) is a systematic methodology 
  for constructing abstract interpreters that are derived from concrete
  small-step abstract machines. Recent progress applies the same idea 
  on definitional interpreters and obtains big-step 
  abstract definitional interpreters (ADI) written in monadic style.
  Yet, the relations between small-step abstracting abstract machines and 
  big-step abstracting definitional interpreters is not well studied.

  In this paper, we show their correspondence and how to syntactically transform small-step 
  abstract abstract machines into big-step abstract definitional 
  interpreters.
  The transformations include linearization, fusing, disentangling, refunctionalizing 
  and monadification (or un-CPS to direct-style). Linearization expresses
  non-deterministic choices into first-order data types, and then refunctionalization
  sequentializes the evaluation order by higher-order functions.
  All of transformations properly handle the collecting semantics and the
  non-determinism of abstract interpretation. 
  %After each transformation, we also obtain an intermediate form of abstract interpreter.

  Following the idea that in deterministic languages,
  evaluation contexts in reduction semantics are defunctionalized continuations,
  we further show in non-deterministic languages, evaluation contexts are refunctionalized to
  extended continuations style.
  Remarkably, we reveal how precise call/return matching in control-flow 
  analysis is obtained by refunctionalizing a small-step abstract
  abstract machine with properly caching.

  %As well as we explain how it been lost by defunctionalizing the higher-order continuations into an first-order data type. 
\end{abstract}
